Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-22 paper/main.tex
add to description of imaging-based comparison

Although this optimization scheme was driven by technical challenges, it is also biologically
motivated.
In the infenitisemal time point after the division event the resulting two daughter cells will cover
precisely the space that the mother had taken up.
Often times, the exact time at which the fission event has commenced can not be determined
accurately, thus leading to uncertainties with respect to the question when the life of the daughter
cells begins and the one of the mother ends.

>>>>

The developed optimization scheme was mainly driven by technical challenges, but it is also
biologically motivated.
In the short time period after the division event, the two resulting daughter cells will cover
the space that the mother had taken up.
Often times, the exact time at which the fission event has commenced can not be determined
accurately, thus leading to uncertainties with respect to the question when the life of the daughter
cells begins and the one of the mother ends.
These uncertainties which are also common problems for segmentation methods, further highlight the
importance of this comparison scheme.
